Figures

### 2020-03-03 figures/07_model-selection.Rmd
add category labels to figure 2

```{r re-comparison, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

@@

cowplot::plot_grid(
cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75)),
ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label)) +
  theme_void(),
ncol = 1, rel_heights = c(1, 0.05))
```

>>>>

```{r re-comparison, fig.width=5}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  mutate(term = factor(term, levels = c("wetlands", "forest", 
                                        "soybeans", "corn", "pasture", "ag")))

label_key <- data.frame(labels = c("Aggregate", "Granular", "Other"), 
                        x = c(0, 0, 0), 
                        y = c(0.62, 0.49, 0.37), 
                        stringsAsFactors = FALSE)
gg_labels <- ggplot() + geom_text(data = label_key, 
                                        aes(x = x, y = y, label = labels), angle = 90) +
    expand_limits(y = c(0.3, 0.7)) +
    theme_void()
gg_tp <- cowplot::plot_grid(gg_labels, 
                   gg_tp, rel_widths = c(0.3, 1))

@@

cowplot::plot_grid(
cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.6)),
ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label)) +
  theme_void(),
ncol = 1, rel_heights = c(1, 0.05))
```
